Dual-Mode PSK Transceiver on SDR With FPGA

### 2024-01-08 latex/_tikz_ila_BPSK.tex
Update Paper

\begin{document}
\begin{figure*}
  \setlength{\tabcolsep}{2pt}
  \sffamily\notsotiny
  \newcommand\Color{mygreen}
  \newcommand\Modulation{BPSK}%
  \newcommand\isBPSK1%
  \begin{tabularx}{\linewidth}{@{}lX@{}}
    DAC\_vld & \input{tikz/ila/DAC_vld} \\
    DAC\_I[11:0] & \input{tikz/ila/DAC_I} \\
    DAC\_Q[11:0] & \input{tikz/ila/DAC_Q} \\
    ADC\_I[11:0] & \input{tikz/ila/ADC_I} \\
    ADC\_Q[11:0] & \input{tikz/ila/ADC_Q} \\
    I\_16M[15:0] & \input{tikz/ila/I_16M} \\
    Q\_16M[15:0] & \input{tikz/ila/Q_16M} \\
    I\_1M[15:0] & \input{tikz/ila/I_1M} \\
    Q\_1M[15:0] & \input{tikz/ila/Q_1M} \\
    DAC\_bits[1:0] & \input{tikz/ila/DAC_bits} \\
    DAC\_bits[1] & \input{tikz/ila/DAC_bits_1} \\
    \textcolor{gray}{DAC\_bits[0]} & \input{tikz/ila/DAC_bits_0} \\
    Rx\_data\_tdata[1:0] & \input{tikz/ila/Rx_data_tdata} \\
    Rx\_data\_tdata[1] & \input{tikz/ila/Rx_data_tdata_1} \\
    \textcolor{gray}{Rx\_data\_tdata[0]} & \input{tikz/ila/Rx_data_tdata_0} \\
    Rx\_data\_tvalid & \input{tikz/ila/Rx_data_tvalid} \\
    Rx\_data\_tlast & \input{tikz/ila/Rx_data_tlast} \\
    Rx\_data\_tuser & \input{tikz/ila/Rx_data_tuser} \\
    Tx\_1bit & \input{tikz/ila/Tx_1bit} \\
    Tx\_vld & \input{tikz/ila/Tx_vld} \\
    Rx\_1bit & \input{tikz/ila/Rx_1bit} \\
    Rx\_vld & \input{tikz/ila/Rx_vld} \\
  \end{tabularx}%
\end{figure*}
\end{document}

>>>>

\begin{document}
\begin{figure*}
  \setlength{\tabcolsep}{2pt}
  \sffamily\notsotiny
  \newcommand\Color{mygreen}
  \newcommand\Modulation{BPSK}%
  \newcommand\isBPSK1%
  \begin{tabularx}{\linewidth}{@{}lX@{}}
    DAC\_vld & \input{tikz/ila/DAC_vld} \\
    DAC\_I[11:0] & \input{tikz/ila/DAC_I} \\
    DAC\_Q[11:0] & \input{tikz/ila/DAC_Q} \\
    ADC\_I[11:0] & \input{tikz/ila/ADC_I} \\
    ADC\_Q[11:0] & \input{tikz/ila/ADC_Q} \\
    I\_16M[15:0] & \input{tikz/ila/I_16M} \\
    Q\_16M[15:0] & \input{tikz/ila/Q_16M} \\
    clk\_1M\_out & \input{tikz/ila/clk_1M_out} \\
    I\_1M[15:0] & \input{tikz/ila/I_1M} \\
    Q\_1M[15:0] & \input{tikz/ila/Q_1M} \\
    DAC\_bits[1:0] & \input{tikz/ila/DAC_bits} \\
    DAC\_bits[1] & \input{tikz/ila/DAC_bits_1} \\
    \textcolor{gray}{DAC\_bits[0]} & \input{tikz/ila/DAC_bits_0} \\
    Rx\_data\_tdata[1:0] & \input{tikz/ila/Rx_data_tdata} \\
    Rx\_data\_tdata[1] & \input{tikz/ila/Rx_data_tdata_1} \\
    \textcolor{gray}{Rx\_data\_tdata[0]} & \input{tikz/ila/Rx_data_tdata_0} \\
    Rx\_data\_tvalid & \input{tikz/ila/Rx_data_tvalid} \\
    Rx\_data\_tlast & \input{tikz/ila/Rx_data_tlast} \\
    Rx\_data\_tuser & \input{tikz/ila/Rx_data_tuser} \\
    Tx\_1bit & \input{tikz/ila/Tx_1bit} \\
    Tx\_vld & \input{tikz/ila/Tx_vld} \\
    Rx\_1bit & \input{tikz/ila/Rx_1bit} \\
    Rx\_vld & \input{tikz/ila/Rx_vld} \\
  \end{tabularx}%
\end{figure*}
\end{document}

### 2024-01-08 latex/_tikz_ila_QPSK.tex
Update Paper

\begin{document}
\begin{figure*}
  \setlength{\tabcolsep}{2pt}
  \sffamily\notsotiny
  \newcommand\Modulation{QPSK}%
  \newcommand\isBPSK0%
  \newcommand\Color{mygreen}
  \begin{tabularx}{\linewidth}{@{}lX@{}}
    DAC\_vld & \input{tikz/ila/DAC_vld} \\
    DAC\_I[11:0] & \input{tikz/ila/DAC_I} \\
    DAC\_Q[11:0] & \input{tikz/ila/DAC_Q} \\
    ADC\_I[11:0] & \input{tikz/ila/ADC_I} \\
    ADC\_Q[11:0] & \input{tikz/ila/ADC_Q} \\
    I\_16M[15:0] & \input{tikz/ila/I_16M} \\
    Q\_16M[15:0] & \input{tikz/ila/Q_16M} \\
    I\_1M[15:0] & \input{tikz/ila/I_1M} \\
    Q\_1M[15:0] & \input{tikz/ila/Q_1M} \\
    DAC\_bits[1:0] & \input{tikz/ila/DAC_bits} \\
    DAC\_bits[1] & \input{tikz/ila/DAC_bits_1} \\
    DAC\_bits[0] & \input{tikz/ila/DAC_bits_0} \\
    Rx\_data\_tdata[1:0] & \input{tikz/ila/Rx_data_tdata} \\
    Rx\_data\_tdata[1] & \input{tikz/ila/Rx_data_tdata_1} \\
    Rx\_data\_tdata[0] & \input{tikz/ila/Rx_data_tdata_0} \\
    Rx\_data\_tvalid & \input{tikz/ila/Rx_data_tvalid} \\
    Rx\_data\_tlast & \input{tikz/ila/Rx_data_tlast} \\
    Rx\_data\_tuser & \input{tikz/ila/Rx_data_tuser} \\
    Tx\_1bit & \input{tikz/ila/Tx_1bit} \\
    Tx\_vld & \input{tikz/ila/Tx_vld} \\
    Rx\_1bit & \input{tikz/ila/Rx_1bit} \\
    Rx\_vld & \input{tikz/ila/Rx_vld} \\
  \end{tabularx}%
\end{figure*}
\end{document}

>>>>

\begin{document}
\begin{figure*}
  \setlength{\tabcolsep}{2pt}
  \sffamily\notsotiny
  \newcommand\Modulation{QPSK}%
  \newcommand\isBPSK0%
  \newcommand\Color{mygreen}
  \begin{tabularx}{\linewidth}{@{}lX@{}}
    DAC\_vld & \input{tikz/ila/DAC_vld} \\
    DAC\_I[11:0] & \input{tikz/ila/DAC_I} \\
    DAC\_Q[11:0] & \input{tikz/ila/DAC_Q} \\
    ADC\_I[11:0] & \input{tikz/ila/ADC_I} \\
    ADC\_Q[11:0] & \input{tikz/ila/ADC_Q} \\
    I\_16M[15:0] & \input{tikz/ila/I_16M} \\
    Q\_16M[15:0] & \input{tikz/ila/Q_16M} \\
    clk\_1M\_out & \input{tikz/ila/clk_1M_out} \\
    I\_1M[15:0] & \input{tikz/ila/I_1M} \\
    Q\_1M[15:0] & \input{tikz/ila/Q_1M} \\
    DAC\_bits[1:0] & \input{tikz/ila/DAC_bits} \\
    DAC\_bits[1] & \input{tikz/ila/DAC_bits_1} \\
    DAC\_bits[0] & \input{tikz/ila/DAC_bits_0} \\
    Rx\_data\_tdata[1:0] & \input{tikz/ila/Rx_data_tdata} \\
    Rx\_data\_tdata[1] & \input{tikz/ila/Rx_data_tdata_1} \\
    Rx\_data\_tdata[0] & \input{tikz/ila/Rx_data_tdata_0} \\
    Rx\_data\_tvalid & \input{tikz/ila/Rx_data_tvalid} \\
    Rx\_data\_tlast & \input{tikz/ila/Rx_data_tlast} \\
    Rx\_data\_tuser & \input{tikz/ila/Rx_data_tuser} \\
    Tx\_1bit & \input{tikz/ila/Tx_1bit} \\
    Tx\_vld & \input{tikz/ila/Tx_vld} \\
    Rx\_1bit & \input{tikz/ila/Rx_1bit} \\
    Rx\_vld & \input{tikz/ila/Rx_vld} \\
  \end{tabularx}%
\end{figure*}
\end{document}

### 2024-01-08 latex/paper.tex
Update Paper

  \begin{abstract}
    In this experiment, we implement a dual-mode PSK transceiver on SDR with FPGA,
    supporting both BPSK and QPSK.
    Moreover, the transceiver is designed to be able to switch between the two modes by introducing packet-based communication,
    where modulation information can be extracted from the packet header.
  \end{abstract}
  \begin{IEEEkeywords}
    Phase-shift keying (PSK), software-defined radio (SDR), transceiver design, modulation, demodulation, field programmable gate array (FPGA).
  \end{IEEEkeywords}

@@

      The BPSK and QPSK modulation constellation graphs used in our system are shown in Fig.~\ref{fig:constellation}.
      Different from the traditional setting, out adopted BPSK constellation in Fig.~\subref*{subfig:constellation_BPSK}
      is a combination of I and Q components.
      This is to make sure the phases used in BPSK are among those in QPSK,
      to ensure a smooth transition between the two modes,
      especially because the header field is always modulated in BPSK.
      \begin{figure}[htbp]
        \subfloat[BPSK.\label{subfig:constellation_BPSK}]{\input{tikz/mod_BPSK}}\hfill%
        \subfloat[QPSK.\label{subfig:constellation_QPSK}]{\input{tikz/mod_QPSK}}
        \caption{BPSK/QPSK modulation constellation used in our system.}
        \label{fig:constellation}
      \end{figure}

@@

      To reduce implementation complexity, we use the sign of strobe values as mentioned in \cite{gardner1986bpsk}.
      The total symbol timing error considering I and Q components is
      \begin{equation}
        \begin{aligned}
          u_t(r)&=y_I(r-\tfrac12)\left[\mathrm{sgn}\left(y_I(r)\right)-\mathrm{sgn}\left(y_I(r-1)\right)\right] \\
          &\quad{}+y_Q(r-\tfrac12)\left[\mathrm{sgn}\left(y_Q(r)\right)-\mathrm{sgn}\left(y_Q(r-1)\right)\right],
        \end{aligned}
      \end{equation}
      where $r$ has a symbol frequency of \qty{1.024}{MHz}.
      For better timing performance, we linearly interpolate the \qty{16.385}{MHz} input I/Q data to \qty{32.768}{MHz}.
      Therefore, $y_I(r-1)$ and $y_Q(r-1)$ are delayed by 32 clocks.
      In FPGA implementation, for each I/Q stream, two shift registers of depth 16 are used.
      Notably, since we adopt the BPSK constellation in Fig.~\subref*{subfig:constellation_BPSK},
      the symbol timing error depends on both I and Q components, the same as QPSK.

@@

    In all Verilog simulation,
    random is added to the Rx ADC, to better simulate the real-world scenario.

@@

      The transmitter DAC simulaiton results are shown in Fig.~\ref{fig:tx_dac_sim}.
      \begin{figure}[h]
        \setlength{\tabcolsep}{2pt}
        \subfloat[BPSK modulation.]{\includegraphics{_tikz_sim_Tx_BPSK-crop.pdf}}\\
        \subfloat[QPSK modulation.]{\includegraphics{_tikz_sim_Tx_QPSK-crop.pdf}}
        \caption{DAC simulation results of the transmitter.}
        \label{fig:tx_dac_sim}
      \end{figure}

      % TODO

@@

@@

    The design is implemented in Vivado 2022.2.

    The hardware resources consumption on Zynq-7020 with the default synthesis and implementation strategy is shown in Table~\ref{tab:resource}.
    Therefore, the design itself is area-efficient, and can be readily incorporated into a larger system.
    \begin{table}[htbp]
      \caption{Hardware Resources Consumption on Zynq-7020}
      \label{tab:resource}
      \renewcommand{\arraystretch}{1.2}
      \rowcolors{1}{white}{gray!15}
      \begin{tabularx}{\linewidth}{YYYY}
        \toprule\tabvertspace
        \textbf{Resource} & \textbf{Utilization} & \textbf{Available} & \textbf{Util.\ Rate} \\
        \tabvertspace\midrule
        LUT & 7,248 & 53,200 & \hphantom{0}8.04\% \\
        LUTRAM & 1,121 & 17,400 & \hphantom{0}6.44\% \\
        FF & 8,144 & 106,400\hphantom{0} & \hphantom{0}7.65\% \\
        BRAM & \hphantom{0,0}27 & \hphantom{00,}140 & 19.29\% \\
        DSP & \hphantom{0,0}51 & \hphantom{00,}220 & 23.18\% \\
        IO & \hphantom{0,0}33 & \hphantom{00,}200 & 16.50\% \\
        BUFG & \hphantom{0,0}10 & \hphantom{00,0}32 & 31.25\% \\
        MMCM & \hphantom{0,00}2 & \hphantom{00,00}4 & 50.00\% \\
        \bottomrule
      \end{tabularx}
    \end{table}

@@

    Fig.~\subref*{subfig:scope_bpsk} and Fig.~\subref*{subfig:scope_qpsk}
    connects the \texttt{GPIO\_TH1} and \texttt{GPIO\_TH2} pins,
    showing the transmitted 1-bit sequence (Tx) and the respective received 1-bit sequence (Rx).
    Clearly, the sequence is successfully recovered in both cases, with a certain time delay.
    The structure of \texttt{pn\_5} sequence in BPSK is clearly seen in Fig.~\subref*{subfig:scope_bpsk},
    which has a bit frequency of \qty{1.024}{MHz}.
    By contrast, the bit frequency of QPSK packets in Fig.~\subref*{subfig:scope_qpsk} is \qty{2.048}{MHz}.

    % sync due to a FIFO

@@

    \begin{figure*}
      \setlength{\tabcolsep}{2pt}
      \subfloat[A BPSK packet.]{\includegraphics{_tikz_ila_BPSK-crop.pdf}}\\
      \subfloat[A QPSK packet.]{\includegraphics{_tikz_ila_QPSK-crop.pdf}}\\
      \caption{System ILA results.}
    \end{figure*}

@@

      \textbf{Frame structure design}.
      CRC and/or checksums can be added to the frame structure.

@@

      The training (TRN) field can be better utilized for additional experiments.
      For example, signal-to-noise (SNR) can be estimated at the TRN field.

      Channel estimation algorithm \cite{zhao2023ompl,you2023beam}.

      Auto generation \cite{zhao2023automatic}.

@@

    In this paper,

@@

  \section{Block Diagrams}

@@

      \begin{figure*}
        \includegraphics[width=\linewidth]{../schematic/top.pdf}
        \caption{Top block diagram.}
      \end{figure*}

@@

      \textbf{AXI connections}.
      1. connection one out of the bus.
      2. \texttt{FREQ\_HZ} property.

      \textbf{Testbenches for block diagrams}.

>>>>

  \begin{abstract}
    In this experiment, we implement a dual-mode PSK transceiver on SDR with FPGA,
    supporting both BPSK and QPSK.
    Moreover, the transceiver is designed to be able to switch between the two modes by introducing packet-based communication,
    where modulation information can be extracted from the packet header.
    Both simulation results and experiment on SDR platforms verify the effectiveness of the design.
  \end{abstract}
  \begin{IEEEkeywords}
    Phase-shift keying (PSK), software-defined radio (SDR), transceiver design, modulation, demodulation, field programmable gate array (FPGA).
  \end{IEEEkeywords}

@@

      The BPSK and QPSK modulation constellation graphs used in our system are shown in Fig.~\ref{fig:constellation}.
      Different from the traditional setting, out adopted BPSK constellation in Fig.~\subref*{subfig:constellation_BPSK}
      is a combination of in-phase (I) and quadrature (Q) components.
      This is to make sure the phases used in BPSK are among those in QPSK,
      to ensure a smooth transition between the two modes,
      especially because the header field is always modulated in BPSK.
      \begin{figure}[htbp]
        \subfloat[BPSK.\label{subfig:constellation_BPSK}]{\input{tikz/mod_BPSK}}\hfill%
        \subfloat[QPSK.\label{subfig:constellation_QPSK}]{\input{tikz/mod_QPSK}}
        \caption{BPSK/QPSK modulation constellation used in our system.}
        \label{fig:constellation}
      \end{figure}

@@

      To reduce implementation complexity, we use the sign of strobe values as mentioned in \cite{gardner1986bpsk}.
      The total symbol timing error considering I and Q components is
      \begin{equation}
        \begin{aligned}
          u_t(r)&=y_I(r-\tfrac12)\left[\mathrm{sgn}\left(y_I(r)\right)-\mathrm{sgn}\left(y_I(r-1)\right)\right] \\
          &\quad{}+y_Q(r-\tfrac12)\left[\mathrm{sgn}\left(y_Q(r)\right)-\mathrm{sgn}\left(y_Q(r-1)\right)\right],
        \end{aligned}
      \end{equation}
      where $r$ has a symbol frequency of \qty{1.024}{MHz}.
      For better timing performance, we linearly interpolate the \qty{16.385}{MHz} input I/Q data to \qty{32.768}{MHz}.
      Therefore, $y_I(r-1)$ and $y_Q(r-1)$ are delayed by 32 clocks.
      In FPGA implementation, for each I/Q stream, two shift registers of depth 16 are used.
      Notably, since we adopt the BPSK constellation in Fig.~\subref*{subfig:constellation_BPSK},
      the symbol timing error depends on both I and Q components, the same as QPSK.
      The correctness of symbol timing is shown in Fig.~\ref{fig:ila}.

    \subsection{PSK Detection}

      The detection is based on the constellation graph in Fig.~\ref{fig:constellation}, and the I/Q signals after the symbol synchronization.

@@

    In all Verilog simulation,
    random noise is added to the Rx ADC, to better simulate the real-world scenario.

@@

      The transmitter DAC simulaiton results are shown in Fig.~\ref{fig:tx_dac_sim}.
      \begin{figure}[htbp]
        \setlength{\tabcolsep}{2pt}
        \subfloat[BPSK modulation.]{\includegraphics{_tikz_sim_Tx_BPSK-crop.pdf}}\\
        \subfloat[QPSK modulation.]{\includegraphics{_tikz_sim_Tx_QPSK-crop.pdf}}
        \caption{DAC simulation results of the transmitter.}
        \label{fig:tx_dac_sim}
      \end{figure}

      Due to the limited number of samples (4 per period), the DAC output is not smooth, and shapes like a triangle wave.
      Nevertheless, the phase shift for both I and Q at symbol transitions is clear.

@@

      The two packets are clearly shown,
      with the first being QPSK and the second being BPSK, both of 128 bits length.
      The \texttt{Rx\_tuser} signal shows the detected modulation scheme at the Rx, with 1 for BPSK and 0 for QPSK.
      Since QPSk has a $2\times$ bit rate, the first packet payload is transmitted $2\times$ faster than the first one.

@@

    The design is implemented in Vivado 2022.2 using block diagrams.
    Some block diagram designs are shown in Section~\ref{sec:block_diagrams}.

    The hardware resources consumption on Zynq-7020 (xc7z020clg484-1)
    with the default synthesis and implementation strategy is shown in Table~\ref{tab:resource}.
    Therefore, the design itself is area-efficient, and can be readily incorporated into a larger system.
    \begin{table}[htbp]
      \caption{Hardware Resources Consumption on Zynq-7020}
      \label{tab:resource}
      \renewcommand{\arraystretch}{1.2}
      \rowcolors{1}{white}{gray!15}
      \begin{tabularx}{\linewidth}{YYYY}
        \toprule\tabvertspace
        \textbf{Resource} & \textbf{Utilization} & \textbf{Available} & \textbf{Util.\ Rate} \\
        \tabvertspace\midrule
        LUT & 7,248 & 53,200 & \hphantom{0}8.04\% \\
        LUTRAM & 1,121 & 17,400 & \hphantom{0}6.44\% \\
        FF & 8,144 & 106,400\hphantom{0} & \hphantom{0}7.65\% \\
        BRAM & \hphantom{0,0}27 & \hphantom{00,}140 & 19.29\% \\
        DSP & \hphantom{0,0}51 & \hphantom{00,}220 & 23.18\% \\
        IO & \hphantom{0,0}33 & \hphantom{00,}200 & 16.50\% \\
        BUFG & \hphantom{0,0}10 & \hphantom{00,0}32 & 31.25\% \\
        MMCM & \hphantom{0,00}2 & \hphantom{00,00}4 & 50.00\% \\
        \bottomrule
      \end{tabularx}
    \end{table}

@@

    Fig.~\subref*{subfig:scope_bpsk} and Fig.~\subref*{subfig:scope_qpsk}
    connects the \texttt{GPIO\_TH1} and \texttt{GPIO\_TH2} pins,
    showing the transmitted 1-bit sequence (Tx) and the respective received 1-bit sequence (Rx).
    Clearly, the sequence is successfully recovered in both cases, with a certain time delay.
    The structure of \texttt{pn\_5} sequence in BPSK is clearly seen in Fig.~\subref*{subfig:scope_bpsk},
    which has a bit frequency of \qty{1.024}{MHz}.
    By contrast, the bit frequency of QPSK packets in Fig.~\subref*{subfig:scope_qpsk} is \qty{2.048}{MHz}.
    The symbol timing clock is shown in Fig.~\subref*{subfig:scope_timing},
    which is not synchronized with the Rx data in BPSK,
    as the Rx data is connected after a FIFO with the master clock of \qty{1.024}{MHz}.

@@

    Fig.~\ref{fig:ila} gives the ILA results for two cases involving BPSK and QPSK.
    The ILA results are consistent with the oscilloscope results,
    and provide additional insight into the system, including PSK detection and packet extraction.
    The \texttt{I\_16M} and the \texttt{Q\_16M} signals are the I and Q components of the baseband signal from the Costas loop,
    while the \texttt{I\_1M} and the \texttt{Q\_1M} signals are provided by the Gardner loop after symbol timing.
    The \texttt{out\_clk\_1M} clock is the symbol timing clock, which is near optimal, as designed by the Gardner loop.

    \begin{figure*}
      \setlength{\tabcolsep}{2pt}
      \subfloat[A BPSK packet.]{\includegraphics{_tikz_ila_BPSK-crop.pdf}}\\
      \subfloat[A QPSK packet.]{\includegraphics{_tikz_ila_QPSK-crop.pdf}}\\
      \caption{System ILA results (some signals not shown). The system ILA has a window of 4,096, at the clock of \qty{32.768}{MHz} (twice the sampling rate).}
      \label{fig:ila}
    \end{figure*}

@@

      \textbf{Frame structure design}.
      CRC and/or checksums can be added to the frame structure to enhance the packet transmission stability.

@@

      The training (TRN) field can be better utilized for additional experiments.
      For example, signal-to-noise (SNR) can be estimated at the TRN field.
      Channel estimation algorithms \cite{zhao2023ompl,you2023beam} can also be investigated on the platform.
      It is also possible to investigate the auto generation \cite{zhao2023automatic} of digital circuits.

@@

    In this paper,
    we implement the PSK transceiver with modulation and demodulation on FPGA.
    It successfully demonstrates the high-level system design,
    and communication techniques such as carrier synchronization, symbol synchronization and packet-based communication.

@@

  \section{Block Diagrams}\label{sec:block_diagrams}

@@

    The top level block diagram corresponding to Fig.~\ref{fig:system_overview} is shown in Fig.~\ref{fig:block_top},
    and the Rx processor block diagram is shown in Fig.~\ref{fig:block_rx}.
    Among the Rx processor, the Costas loop and the Gardner are both inserted block diagrams.
    \begin{figure*}
      \includegraphics[width=\linewidth]{../schematic/top.pdf}
      \caption{Top block diagram.}
      \label{fig:block_top}
    \end{figure*}
    \begin{figure*}
      \includegraphics[width=\linewidth]{../schematic/Rx.pdf}
      \caption{Rx processor block diagram.}
      \label{fig:block_rx}
    \end{figure*}

    The costas loop is shown in Fig.~\ref{fig:block_costas_looop},
    where the phase detectors are implemented using the multiplier IP.

    \begin{figure*}
      \includegraphics[width=\linewidth]{../schematic/costas_loop.pdf}
      \caption{Costas loop block diagram for carrier synchronization.}
      \label{fig:block_costas_looop}
    \end{figure*}

    More block diagrams are provided at \url{https://github.com/Teddy-van-Jerry/sdr-psk-fpga} \cite{github_repo}.

@@

      \textbf{AXI connections}.
      AXI and AXI stream (AXIS) interfaces should be carefully dealt with in the block diagram.
      When connecting one of the signal in the bus elsewhere (e.g., to ILA),
      ar manual connection of the signal to the corresponding AXIS interface signal is required.
      Besides, when the AXI interface is not associated with a clock (for example a combinational logic with no register output)
      the \texttt{FREQ\_HZ} property needs to be correctly set before validating the design.

      \textbf{Testbenches for block diagrams}.
      It is relatively difficult to simulate block diagrams than Verilog modules.
      The possible way is to generate the output products and find the correct module (name containing \texttt{impl}).
      Be careful when adding sources for simulation, and Tcl scripts are provided in \cite{github_repo} to ensure the correctness.
      Vivado can be buggy when updating sources from the block diagram (for both simulation and implementation),
      and therefore it is advised to double-check the netlist file timestamp.
